---
title: "REINVENT Data"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: false
      smooth_scroll: true
    number_sections: false
    code_folding: hide
    fig_width: 7
    fig_height: 4
    fig_caption: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r RestartEnvironment, echo = FALSE}
rm(list=ls())
graphics.off()
cat("\014")
```

```{r Libraries, echo = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(reshape2)
library(pander)
```

```{r InitialSetup}

# Colors
seqColor <- c("#a6611a","#dfc27d","#80cdc1","#018571")

# Figure Theme
figTheme <- theme(
  legend.text = element_text(size = 12),
  legend.title = element_text(size = 12),
  plot.title = element_text(size = 12),
  strip.text.x = element_text(size = 12),
  axis.title.x = element_text(size = 12),
  axis.title.y = element_text(size = 12),
  axis.text.x = element_text(size = 12),
  axis.text.y = element_text(size = 12))

# Load data frame
load("sensors2020data.Rda")

```

***

# Table 1

Participant demographics and baseline evaluations
```{r Demographics}

# Show table
demograph.data%>%
  dplyr::rename(
    "Participant" = Subject,
    "Sex" = Gender,
    "Onset (months)" = Months.since.stroke,
    "FMA-UE" = FMA,
    "Paresis" = Affected.side) %>%
  pander()

```


# Feasibility

The simulator sickness questionnaire evaluates different components and has a total score of 63 points. 
Group changes on simulator sickness were evaluated with the total sickness as a percentage (sickness = total*100/63).
```{r SimulatorSickness}

# Get pre and post 
pre <- simsick.data %>%
  filter(session == 2)
post <- simsick.data %>%
  filter(session == 9)

t.test(post$Sickness, pre$Sickness, paired = TRUE)

```


# Figure 2

Clinical Assessments
```{r ClinicalAssessments}

# Change session to Pre-Post and melt dataframe
behav.melt <- 
  behav.data %>%
  filter(session %in% c(1,10)) %>%
  mutate(session = ifelse(session == 1, "Pre","Post")) %>%
  dplyr::rename(
    "Extension" = WE,
    "SIS-16" = SIS16) %>%
  melt(id = c("subject","session"))

# Plot FMA and ARAT
behav.melt %>%
  ggplot() +
  geom_line(aes(session, value, group = as.factor(subject), color = as.factor(subject)), size = 2, alpha = 0.7, show.legend = F) +
  geom_point(aes(session, value, shape = as.factor(subject), fill = as.factor(subject)), size = 3) +
  
  facet_wrap(~ variable, scales = "free", ncol = 3) +
  xlab("Evaluation") +
  ylab("") +
  theme_classic() +
  scale_x_discrete(limits = c("Pre","Post")) +
  scale_color_manual(values = seqColor[1:5]) +
  scale_fill_manual(values = seqColor[1:5]) +
  scale_shape_manual(values = 21:24) +
  figTheme +
  theme( strip.background.x = element_blank())+
  labs(
    title = "Clinical Assessments",
    fill = "Participant",
    shape = "Participant",
    color = ""
  )
```


# Table 2

Statistical comparisons for clinical assessments
```{r ClinicalAssessmentsGroup}
# Sumary of t test per assessment
aux = TRUE
for (scale in c("FMA","ARAT","WE","GripMore","SIS16")) {
  
  pre <-
    behav.data %>%
    filter(session == 1) %>%
    pull(scale)
  post <-
    behav.data %>%
    filter(session == 10) %>%
    pull(scale)
  
  tt <- t.test(post, pre, paired = TRUE)
  
  if(aux){
    t <- data.frame(Assessment = scale, t = tt$statistic, p = tt$p.value,
                    Pre = paste(mean(pre, na.rm = T)," (",formatC(sd(pre, na.rm = T),digits = 5),")",sep = ""),
                    Post = paste(mean(post, na.rm = T)," (",formatC(sd(post, na.rm = T),digits = 5),")",sep = ""))
    aux = FALSE
  }
  else{
    t <- bind_rows(t,data.frame(Assessment = scale, t = tt$statistic, p = tt$p.value,
                                Pre = paste(mean(pre, na.rm = T)," (",formatC(sd(pre, na.rm = T),digits = 5),")",sep = ""),
                                Post = paste(mean(post, na.rm = T)," (",formatC(sd(post, na.rm = T),digits = 5),")",sep = "")))
  }
}

scaleName = c("FMA","ARAT","Extension","Grip More-Imp.","SIS-16")
t$Assessment <- scaleName

# As table
t %>%
  arrange(Assessment) %>%
  pander()

```


# Figure 3

* Individual statistics were calculated within the Matlab script that processed the tracking error from the target.
```{r TrackingErrorStats}

# Individual stats
track.data %>%
  filter(session == "Post",metric == "Error") %>%
  select(-c(session,metric,value)) %>%
  pander()

# Group t-test
aux = TRUE

for (tk in c("Extension","Flexion")) {
  pre <- track.data %>%
    filter(session == "Pre",metric == "Error", task == tk) %>%
    pull(value)
  post <- track.data %>%
    filter(session == "Post",metric == "Error", task == tk) %>%
    pull(value)
  
  tt <- t.test(post, pre, paired = TRUE)
  
  if(aux){
    t <- data.frame(task = paste(tk,"Error",sep = " "), t = tt$statistic, p = tt$p.value,
                    Pre = paste(mean(pre, na.rm = T)," (",formatC(sd(pre, na.rm = T),digits = 5),")",sep = ""),
                    Post = paste(mean(post, na.rm = T)," (",formatC(sd(post, na.rm = T),digits = 5),")",sep = ""))
    aux = FALSE
  }
  else{
    t <- bind_rows(t,data.frame(task = paste(tk,"Error",sep = " "), t = tt$statistic, p = tt$p.value,
                                Pre = paste(mean(pre, na.rm = T)," (",formatC(sd(pre, na.rm = T),digits = 5),")",sep = ""),
                                Post = paste(mean(post, na.rm = T)," (",formatC(sd(post, na.rm = T),digits = 5),")",sep = "")))
  }
}

t %>%
  dplyr::rename("Task" = task) %>%
  pander()
```

Performance changes in EMG amplitude control.
```{r TrackingError}
# Mean Amplitude Error
track.error <-
  track.data %>%
  filter(metric == "Error") %>%
  select(-c(metric,p)) %>%
  dplyr::rename("error" = value, "subject" = participant)

# Standard Deviation
track.dev <-
  track.data %>%
  filter(metric == "Deviation")

track.error$lowSD <- track.error$error-track.dev$value
track.error$upSD <- track.error$error+track.dev$value


track.error %>%
  ggplot() +
  geom_bar(aes(session,error, fill = as.factor(subject) ), stat = "identity", position = "dodge") +
  geom_errorbar(aes(session,error,ymin = lowSD, ymax = upSD)) +
  
  facet_wrap(task ~ subject, scales = "free_x", ncol = 4, strip.position = "left") +
  xlab("Evaluation") +
  ylab("") +
  theme_classic() +
  scale_x_discrete(limits = c("Pre","Post")) +
  scale_color_manual(values = seqColor[1:4]) +
  scale_fill_manual(values = seqColor[1:4]) +
  scale_shape_manual(values = 21:24) +
  figTheme +
  theme( strip.background.y = element_blank(),
         legend.text = element_blank())+
  labs(
    title = "Tracking Error",
    fill = "",
    shape = "",
    color = ""
  )
```



# Table 3

Group level analysis of within-game performance andd grip strenght across trqaining sessions.
```{r ActivityGroup}

aux = TRUE
for (scale in c("extensors","flexors","individuation","threshold","success","grip")) {
  
  pre <-
    training.data %>%
    filter(session == 3) %>%
    pull(scale)
  post <-
    training.data %>%
    filter(session == 9) %>%
    pull(scale)
  
  tt <- t.test(post, pre, paired = TRUE)
  
  if(aux){
    t <- data.frame(Activity = scale, t = tt$statistic, p = tt$p.value,
                    Pre = paste(formatC(mean(pre, na.rm = T),digits = 5)," (",formatC(sd(pre, na.rm = T),digits = 5),")",sep = ""),
                    Post = paste(formatC(mean(post, na.rm = T),digits = 5)," (",formatC(sd(post, na.rm = T),digits = 5),")",sep = ""))
    aux = FALSE
  }
  else{
    t <- bind_rows(t,data.frame(Activity = scale, t = tt$statistic, p = tt$p.value,
                                Pre = paste(formatC(mean(pre, na.rm = T),digits = 5)," (",formatC(sd(pre, na.rm = T),digits = 5),")",sep = ""),
                                Post = paste(formatC(mean(post, na.rm = T),digits = 5)," (",formatC(sd(post, na.rm = T),digits = 5),")",sep = "")))
  }
}

t %>%
  arrange(p) %>%
  pander()

```



# Figure 5
Muscle activity and performance during training

* Both plots show the extensor activity (as Z score) the extensor ratio (as Z score) and the success rate (as percentage). Two plots were created for easier visualization of both scales (-2 to 6, and 0 to 100) and then edited to a single figure. 
```{r Activity}

training.data %>%
  select(c("subject","session","extensors","individuation","success")) %>%
  melt(id = c("subject","session")) %>%
  ggplot() +
  geom_point(aes(session, value, shape = as.factor(subject), fill = as.factor(subject)), size = 2) +
  geom_smooth(aes(session, value), method = 'lm', se = FALSE) + 
  
  facet_wrap(variable ~ subject, nrow = 5, ncol = 4) +
  xlab("") +
  ylab("") +
  theme_classic() +
  scale_y_continuous(limits = c(-2,6)) +
  scale_color_manual(values = seqColor[c(1:4)]) +
  scale_fill_manual(values = seqColor[c(1:4)]) +
  scale_shape_manual(values = 21:24) +
  figTheme +
  theme(
    strip.background.x = element_blank(),
    strip.text.x = element_blank(),
    legend.text = element_blank()
  )+
  labs(
    title = "Reinvent Activity",
    fill = "Participant",
    shape = "Participant"
  )

training.data %>%
  select(c("subject","session","extensors","individuation","success")) %>%
  melt(id = c("subject","session")) %>%
  ggplot() +
  geom_point(aes(session, value, shape = as.factor(subject), fill = as.factor(subject)), size = 2) +
  geom_smooth(aes(session, value), method = 'lm', se = FALSE) + 
  
  facet_wrap(variable ~ subject, nrow = 5, ncol = 4) +
  xlab("") +
  ylab("") +
  theme_classic() +
  scale_y_continuous(limits = c(0,100)) +
  scale_color_manual(values = seqColor[c(1:4)]) +
  scale_fill_manual(values = seqColor[c(1:4)]) +
  scale_shape_manual(values = 21:24) +
  figTheme +
  theme(
    strip.background.x = element_blank(),
    strip.text.x = element_blank(),
    legend.text = element_blank()
  )+
  labs(
    title = "Reinvent Activity",
    fill = "Participant",
    shape = "Participant"
  )
```




```{r ActivityCorrelation}

training.nested <-
  training.data %>%
  as_tibble() %>%
  group_by(subject) %>%
  nest()

print("Extensors session correlation")
training.nested %>%
  mutate(
    test = purrr::map(data, ~cor.test(.x$session, .x$extensors, method = "spearman")),
    tidied = purrr::map(test,tidy)
  ) %>%
  unnest(tidied) %>%
  select(c("subject", "estimate","p.value")) %>%
  dplyr::rename("Participant"=subject, "rho"=estimate, "p"=p.value)%>%
  pander()

print("Flexors session correlation")
training.nested %>%
  mutate(
    test = purrr::map(data, ~cor.test(.x$session, .x$flexors, method = "spearman")),
    tidied = purrr::map(test,tidy)
  ) %>%
  unnest(tidied) %>%
  select(c("subject", "estimate","p.value")) %>%
  dplyr::rename("Participant"=subject, "rho"=estimate, "p"=p.value)%>%
  pander()

print("ER session correlation")
training.nested %>%
  mutate(
    test = purrr::map(data, ~cor.test(.x$session, .x$individuation, method = "spearman")),
    tidied = purrr::map(test,tidy)
  ) %>%
  unnest(tidied) %>%
  select(c("subject", "estimate","p.value")) %>%
  dplyr::rename("Participant"=subject, "rho"=estimate, "p"=p.value)%>%
  pander()

print("Threshold session correlation")
training.nested %>%
  mutate(
    test = purrr::map(data, ~cor.test(.x$session, .x$threshold, method = "spearman")),
    tidied = purrr::map(test,tidy)
  ) %>%
  unnest(tidied) %>%
  select(c("subject", "estimate","p.value")) %>%
  dplyr::rename("Participant"=subject, "rho"=estimate, "p"=p.value)%>%
  pander()

print("Performance session correlation")
training.nested %>%
  mutate(
    test = purrr::map(data, ~cor.test(.x$session, .x$success, method = "spearman")),
    tidied = purrr::map(test,tidy)
  ) %>%
  unnest(tidied) %>%
  select(c("subject", "estimate","p.value")) %>%
  dplyr::rename("Participant"=subject, "rho"=estimate, "p"=p.value)%>%
  pander()

print("Grip session correlation")
training.nested %>%
  mutate(
    test = purrr::map(data, ~cor.test(.x$session, .x$grip, method = "spearman")),
    tidied = purrr::map(test,tidy)
  ) %>%
  unnest(tidied) %>%
  select(c("subject", "estimate","p.value")) %>%
  dplyr::rename("Participant"=subject, "rho"=estimate, "p"=p.value)%>%
  pander()
```
